---
title: 1 Basics
author: Adriano Rutz
creative_commons: CC BY-SA
date: "`r Sys.Date()`"
opengraph:
    image:
      src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
      alt: Contextualizing untargeted Annotation with Semi-quantitative Charged Aerosol Detection for pertinent characterization of natural Extracts
    twitter:
      creator: "@adafede"
vignette: >
  %\VignetteIndexEntry{1 Basics}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
knitr::opts_knit$set(root.dir = system.file(package = "cascade"))
```

```{r cascade, include = FALSE}
library("cascade")
```

This vignette describes some basic functions.

## Check the raw data and alignment

First, check if the raw data can be aligned to your expectations:

```{r check-alignment-default, echo=FALSE, message=FALSE, warning=FALSE}
check_chromatograms_alignment(show_example = TRUE)
```

Or, with more details:

```{r check-alignment-2, echo=FALSE, message=FALSE, warning=FALSE}
check_chromatograms_alignment(
  show_example = TRUE,
  time_min = 0.5,
  time_max = 35.0,
  type = "improved",
  chromatograms = c(
    "bpi_pos",
    "cad_pos",
    "pda_pos",
    "bpi_neg",
    "cad_neg",
    "pda_neg"
  )
)
```

How it should not look like (CAD and PDA shifts incorrectly set):

```{r check-alignment-3, echo=FALSE, message=FALSE, warning=FALSE}
check_chromatograms_alignment(
  show_example = TRUE,
  time_min = 0.5,
  time_max = 35.0,
  cad_shift = 1,
  pda_shift = 2,
  type = "baselined",
  chromatograms = c(
    "bpi_pos",
    "cad_pos",
    "pda_pos"
  )
)
```

## Check the peak integration

Another critical parameter is the peak integration.
Below are some illustrations:

```{r check-integration-1, echo=FALSE, message=FALSE, warning=FALSE}
check_peaks_integration(
  show_example = TRUE,
  chromatogram = "improved"
)
```

Some peaks are still missed but it looks overall correct.

Depending on the runs, this can get slightly better with baseline correction:

```{r check-integration-2, echo=FALSE, message=FALSE, warning=FALSE}
check_peaks_integration(
  show_example = TRUE
)
```

We now recommend you to read the [next vignette](https://adafede.github.io/cascade/articles/II-processing.html).

