---
title: 1 Basics
author:
  name: Adriano Rutz
  orcid: 0000-0003-0443-9902
citation:
  url: https://adafede.github.io/cascade/vignettes/articles/I-basics.html
comments:
  giscus:
    repo: adafede/cascade
  hypothesis:
    showHighlights: always
creative_commons: CC BY
date: today
format:
  html:
    smooth-scroll: true
google-scholar: true
knitr:
  opts_chunk:
    collapse: true
    comment: "#>"
lang: en
license: CC BY
opengraph:
  image:
    src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
    alt: Contextualizing untargeted Annotation with Semi-quantitative Charged
      Aerosol Detection for pertinent characterization of natural Extracts
vignette: >
  %\VignetteIndexEntry{1 Basics}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: cascade
#| include: false

library("cascade")
```

This vignette describes some basic functions.

## Check the raw data and alignment

First, check if the raw data can be aligned to your expectations:

```{r}
#| label: check-alignment-default
#| message: false
#| warning: false

check_chromatograms_alignment(show_example = TRUE)
```

Or, with more details:

```{r}
#| label: check-alignment-2
#| message: false
#| warning: false

check_chromatograms_alignment(
  show_example = TRUE,
  time_min = 0.5,
  time_max = 35.0,
  type = "improved",
  chromatograms = c(
    "bpi_pos",
    "cad_pos",
    "pda_pos",
    "bpi_neg",
    "cad_neg",
    "pda_neg"
  )
)
```

How it should not look like (CAD and PDA shifts incorrectly set):

```{r}
#| label: check-alignment-3
#| message: false
#| warning: false

check_chromatograms_alignment(
  show_example = TRUE,
  time_min = 0.5,
  time_max = 35.0,
  cad_shift = 1,
  pda_shift = 2,
  type = "baselined",
  chromatograms = c(
    "bpi_pos",
    "cad_pos",
    "pda_pos"
  )
)
```

## Check the peak integration

Another critical parameter is the peak integration. Below are some
illustrations:

```{r}
#| label: check-integration-1
#| message: false
#| warning: false

check_peaks_integration(
  show_example = TRUE,
  chromatogram = "improved"
)
```

Some peaks are still missed but it looks overall correct.

Depending on the runs, this can get slightly better with baseline correction:

```{r}
#| label: check-integration-2
#| message: false
#| warning: false

check_peaks_integration(
  show_example = TRUE
)
```

We now recommend you to read the [next
vignette](https://adafede.github.io/cascade/vignettes/articles/II-processing.html).
