---
title: 2 Processing
author:
  name: Adriano Rutz
  orcid: 0000-0003-0443-9902
citation:
  url: https://adafede.github.io/cascade/articles/vignettes/II-processing.html
comments:
  giscus:
    repo: adafede/cascade
  hypothesis:
    showHighlights: always
creative_commons: CC BY
date: today
format:
  html:
    smooth-scroll: true
google-scholar: true
knitr:
  opts_chunk:
    collapse: true
    comment: "#>"
lang: en
license: CC BY
opengraph:
  image:
    src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
    alt: Contextualizing untargeted Annotation with Semi-quantitative Charged
      Aerosol Detection for pertinent characterization of natural Extracts
vignette: >
  %\VignetteIndexEntry{2 Processing}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r}
#| label: cascade
#| include: false

library("cascade")
```

This vignette describes the main processing function. It assumes you already
checked the [previous basic
steps](https://adafede.github.io/cascade/articles/I-basics.html).

## Compare peaks to features

To do so, you will need:

- A previously generated mzmine features' table

Then, you should be able to run

```{r}
#| label: process-compare-peaks
#| warning: false

process_compare_peaks(show_example = TRUE)
```

And this basically it! 🚀

## Pseudo chromatograms

If you know want to add some cosmetics, and you already have a
[TIMA](https://taxonomicallyinformedannotation.github.io/tima) annotation table,
you can then run:

```{r}
#| label: generate-pseudochromatograms
#| message: false
#| warning: false

plots_list <- generate_pseudochromatograms(show_example = TRUE)
```

The different plots offer the following views:

### Taxo (major peaks)

```{r}
#| label: taxo-major
#| warning: false
#| dev: svglite

plots_list$plots_1$histograms_taxo_maj
```

### Taxo (minor peaks)

```{r}
#| label: taxo-minor
#| warning: false
#| dev: svglite

plots_list$plots_1$histograms_taxo_min
```

### Confident unique annotations (major)

```{r}
#| label: confident-major
#| warning: false
#| dev: svglite

plots_list$plots_1$histograms_unique_conf_maj
```

### Confident unique annotations (minor)

```{r}
#| label: unique-minor
#| warning: false
#| dev: svglite

plots_list$plots_1$histograms_unique_conf_min
```

Or getting rid of the chromatogram:

### Treemap semi-quantitative (major)

```{r}
#| label: treemap-major
#| warning: false
#| dev: svglite

plots_list$treemaps$peaks_maj
```

### Treemap semi-quantitative (minor)

```{r}
#| label: treemap-minor
#| warning: false
#| dev: svglite

plots_list$treemaps$peaks_min
```

Or both together for comparison:

### Treemap both

```{r}
#| label: treemap-both
#| warning: false
#| dev: svglite

plots_list$treemaps$special
```

## Tabular reports

If you prefer tables rather than figures, you can also:

```{r}
#| label: generate-tables
#| message: false
#| warning: false

tables_list <- generate_tables(show_example = TRUE)
```

This will export the table as CSV and/or HTML. A small preview of the HTML table
is presented below:

```{r}
#| label: glimpse-tables
#| message: false
#| warning: false
#| dev: svglite

tables_list$pretty_table
```

For some other available helper functions, we now recommend you to read the
[next
vignette](https://adafede.github.io/cascade/vignettes/articles/III-bonus.html).
