---
title: 2 Processing
author: 
  - name: Adriano Rutz
    orcid: 0000-0003-0443-9902
comments:
  hypothesis:
    showHighlights: always
creative_commons: CC BY-SA
date: "`r Sys.Date()`"
format:
  html:
    # code-links:
    #  - repo: https://github.com/adafede/cascade
    smooth-scroll: true
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
opengraph:
    image:
      src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
      alt: Contextualizing untargeted Annotation with Semi-quantitative Charged Aerosol Detection for pertinent characterization of natural Extracts
vignette: >
  %\VignetteIndexEntry{2 Processing}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r cascade, include = FALSE}
library("cascade")
```

This vignette describes the main processing function.
It assumes you already checked the [previous basic steps](https://adafede.github.io/cascade/articles/I-basics.html).

## Compare peaks to features

To do so, you will need:

- A previously generated mzmine features' table

Then, you should be able to run

```{r process-compare-peaks, warning=FALSE}
process_compare_peaks(show_example = TRUE)
```

And this basically it! 🚀

## Pseudo chromatograms

If you know want to add some cosmetics, and you already have a [TIMA](https://taxonomicallyinformedannotation.github.io/tima) annotation table, you can then run:

```{r generate-pseudochromatograms, message = FALSE, warning=FALSE}
plots_list <- generate_pseudochromatograms(show_example = TRUE)
```

The different plots offer the following views:

### Taxo (major peaks)

```{r taxo-major, warning=FALSE}
plots_list$plots_1$histograms_taxo_maj
```

### Taxo (minor peaks)

```{r taxo-minor, warning=FALSE}
plots_list$plots_1$histograms_taxo_min
```

### Confident unique annotations (major)

```{r confident-major, warning=FALSE}
plots_list$plots_1$histograms_unique_conf_maj
```

### Confident unique annotations (minor)

```{r unique-minor, warning=FALSE}
plots_list$plots_1$histograms_unique_conf_min
```

Or getting rid of the chromatogram:

### Treemap semi-quantitative (major)

```{r treemap-major, warning=FALSE}
plots_list$treemaps$peaks_maj
```

### Treemap semi-quantitative (minor)

```{r treemap-minor, warning=FALSE}
plots_list$treemaps$peaks_min
```

Or both together for comparison:

### Treemap both

```{r treemap-both, warning=FALSE}
plots_list$treemaps$special
```

## Tabular reports

If you prefer tables rather than figures, you can also:

```{r generate-tables, message = FALSE, warning=FALSE}
tables_list <- generate_tables(show_example = TRUE)
```

This will export the table as CSV and/or HTML.
A small preview of the HTML table is presented below:

```{r glimpse-tables, message = FALSE, warning=FALSE}
tables_list$pretty_table
```

For some other available helper functions, we now recommend you to read the [next vignette](https://adafede.github.io/cascade/articles/III-bonus.html).
