---
title: "2 Processing"
author: "Adriano Rutz"
creative_commons: CC BY-SA
date: "`r Sys.Date()`"
knitr:
  opts_chunk: 
    collapse: true
    comment: "#>"
  opts_knit: 
    set:
      root.dir:
        system.file:
          package: "cascade"
opengraph:
    image:
      src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
      alt: Contextualizing untargeted Annotation with Semi-quantitative Charged Aerosol Detection for pertinent characterization of natural Extracts
    twitter:
      creator: "@adafede"
vignette: >
  %\VignetteIndexEntry{2 Processing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r cascade, include = FALSE}
library("cascade")
```

This vignette describes the main processing function.
It assumes you already checked the [previous basic steps](https://adafede.github.io/cascade/articles/I-basics.html).

## Compare peaks to features

To do so, you will need:

- A previously generated mzmine features' table

Then, you should be able to run

```{r process-compare-peaks, warning=FALSE}
process_compare_peaks(show_example = TRUE)
```

And this basically it! 🚀

If you know want to add some cosmetics, and you already have a [TIMA](https://taxonomicallyinformedannotation.github.io/tima) annotation table, you can then run:

```{r process-plot-pseudochromatograms, message = FALSE, warning=FALSE}
plots_list <- process_plot_pseudochromatograms(show_example = TRUE)
```

The different plots offer the following views:

### Taxo (major peaks)

```{r taxo-major, warning=FALSE}
plots_list$plots_1$histograms_taxo_maj
```

### Taxo (minor peaks)

```{r taxo-minor, warning=FALSE}
plots_list$plots_1$histograms_taxo_min
```

### Confident unique annotations (major)

```{r confident-major, warning=FALSE}
plots_list$plots_1$histograms_unique_conf_maj
```

### Confident unique annotations (minor)

```{r unique-minor, warning=FALSE}
plots_list$plots_1$histograms_unique_conf_min
```

Or getting rid of the chromatogram:

### Treemap semi-quantitative (major)

```{r treemap-major, warning=FALSE}
plots_list$treemaps$peaks_maj
```

### Treemap semi-quantitative (minor)

```{r treemap-minor, warning=FALSE}
plots_list$treemaps$peaks_min
```

Or both together for comparison:

### Treemap both

```{r treemap-both, warning=FALSE}
plots_list$treemaps$special
```

For some other available helper functions, we now recommend you to read the [next vignette](https://adafede.github.io/cascade/articles/III-bonus.html).
