---
title: 3 Bonus
author: 
  name: Adriano Rutz
  orcid: 0000-0003-0443-9902
citation:
  url: https://adafede.github.io/cascade/articles/III-bonus.html
comments:
  giscus: 
    repo: adafede/cascade
  hypothesis:
    showHighlights: always
creative_commons: CC BY-SA
date: today
format:
  html:
    smooth-scroll: true
google-scholar: true
lang: en
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
opengraph:
    image:
      src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
      alt: Contextualizing untargeted Annotation with Semi-quantitative Charged Aerosol Detection for pertinent characterization of natural Extracts
vignette: >
  %\VignetteIndexEntry{3 Bonus}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r cascade, include = FALSE}
library("cascade")
```

This vignette describes some additional bonus helper functions.
A lot of it is based on previous work done in the frame of the [LOTUS initiative](https://doi.org/10.7554/eLife.70780).

## Quick overview of the literature

To check (and eventually compare to your own results) what is known in the literature about different organisms:

```{r wikidata-plots, message = FALSE, warning=FALSE}
bonus_plots_list <- generate_ids(
  taxa = c("Swertia", "Kopsia", "Ginkgo"),
  comparison = c("Swertia", "Kopsia"),
  no_stereo = TRUE,
  filter_ms_conditions = TRUE,
  start = "1950",
  end = "2025"
)
```

### Compounds found in Swertia 

```{r wikidata-swertia-1, warning=FALSE, fig.height=5}
bonus_plots_list$plots$Swertia
```

### Compounds found in Kopsia (per species)

```{r wikidata-kopsia-1, warning=FALSE}
bonus_plots_list$plots$Kopsia_grouped
```

### Comparison

```{r wikidata-swertia-kopsia, warning=FALSE, fig.height=6}
bonus_plots_list$plots$special
```

We hope you enjoyed using **CASCADE** and are pleased to hear from you!

For any remark or suggestion, please  [fill an issue](https://github.com/adafede/cascade/issues) or feel free to contact us directly.
