---
title: 4 Visualizing raw TIMA results
author: 
  name: Adriano Rutz
  orcid: 0000-0003-0443-9902
citation:
  url: https://adafede.github.io/cascade/articles/IV-tima.html
comments:
  hypothesis:
    showHighlights: always
creative_commons: CC BY-SA
date: today
format:
  html:
    # code-links:
    #  - repo: https://github.com/adafede/cascade
    smooth-scroll: true
google-scholar: true
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
lang: en
opengraph:
    image:
      src: https://github.com/adafede/cascade/blob/main/man/figures/logo.svg
      alt: Contextualizing untargeted Annotation with Semi-quantitative Charged Aerosol Detection for pertinent characterization of natural Extracts
vignette: >
  %\VignetteIndexEntry{4 TIMA}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

```{r cascade, include = FALSE}
library("cascade")
```

This vignette describes additional helper functions to visualize [TIMA](https://taxonomicallyinformedannotation.github.io/tima/) results.

## Visualization

To check the full results:

```{r tima-plots, message = FALSE, warning=FALSE}
plots <- cascade::prepare_tima_annotations(
  show_example = TRUE
) |> 
  cascade::plot_tima()
# cascade::prepare_tima_annotations(
#   annotations = list(
#     "yourExperiment1"="PathToYourTimaOutput1",
#     "yourExperiment2"="PathToYourTimaOutput2"
#     )
# ) |> 
#   cascade::plot_tima()
```
```{r tima-plots-h, message = FALSE, warning=FALSE, fig.height=10}
plots$histogram
```

```{r tima-plots-t, message = FALSE, warning=FALSE, fig.height=10}
plots$treemap
```

```{r tima-plots-s, message = FALSE, warning=FALSE, fig.height=10}
plots$sunburst
```

To compare annotated and predicted classes:

```{r tima-plots-1, warning=FALSE, fig.height=10}
list(
  cascade::prepare_tima_annotations(
    show_example = TRUE
    ),
  cascade::prepare_tima_annotations(
    show_example = TRUE,
    predicted_classes = TRUE
    )
  ) |>
  tidytable::bind_rows() |>
  list() |>
  cascade::plot_tima() |>
  purrr::pluck("histogram")
```

To compare different filtering thresholds:

```{r tima-plots-2, warning=FALSE, fig.height=10}
list(
  cascade::prepare_tima_annotations(
    show_example = TRUE
  ), 
  cascade::prepare_tima_annotations(
    show_example = TRUE,
    min_score_biological = 0.2,
    min_score_final = 0.4
  ),
  cascade::prepare_tima_annotations(
    show_example = TRUE,
    min_score_initial = 0.2,
    min_score_biological = 0.2,
    min_score_chemical = 0.2,
    min_score_final = 0.4,
    min_matched_peaks_absolute = 6L,
    min_matched_peaks_percentage = 0.5,
    min_peaks = 10L
    )
  ) |>
  tidytable::bind_rows() |>
  list() |> 
  cascade::plot_tima() |>
  purrr::pluck("histogram")
```

We hope you enjoyed using **CASCADE** and are pleased to hear from you!

For any remark or suggestion, please  [fill an issue](https://github.com/adafede/cascade/issues) or feel free to contact us directly.
